The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
updates to FThresholds paper introduction

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.  Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  The $\fpt$ of $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.  As a further generalization, the notion of \emph{$F$-threshold} was also introduced.  All of these \emph{thresholds} have been the focus of intense study over the past 15 years.

@@

\noindent {\it Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.  We thank the organizers of the five \emph{Macaulay2} workshops where much of the functionality in the package was develope, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016. 
Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.

>>>>

After the advent of tight closure \cite{HochsterHunekeTC1}, the usage of the Frobenius endomorphism to measure singularities proliferated, and based on a strong connection discovered between $F$-pure and \emph{log canonical} singularities \cite{HaraWatanabeFRegFPure}, the notion of $F$-purity was generalized to pairs $(R, f^t)$, where $f$ is an element of $R$, and $t$ is a positive rational number $t$ considered as a formal exponent.  Along these lines, the notion of the \emph{$F$-pure threshold} (or $\fpt$) was defined in analogy with the log canonical threshold (or $\lct$) \cite{TakagiWatanabeFPureThresh,MustataTakagiWatanabeFThresholdsAndBernsteinSato}.  The $\fpt$ of $(R, f)$ is the supremum over all $t$ for which $(R, f^t)$ is $F$-pure, and the functionality computing this number is the core of this package.  As a further generalization, the notion of \emph{$F$-threshold} was also introduced.  All of these \emph{thresholds} have been the focus of intense study over the past fifteen years.

@@

\subsection*{Acknowledgements.}  First and foremost, the authors enthusiastically thank all contributors to the \emph{FThresholds} package:  Erin Bela, Juliette Bruce, Zhibek Kadyrsizova, Sara Malec, Maral Mostafazadehfard, Marcus Robinson, Dan Smolkin, and Robert Walker.  We are also grateful the organizers of the \emph{Macaulay2} workshops where much of the functionality described herein was developed, hosted by Wake Forest University in 2012, the University of California, Berkeley in 2014 and 2017, Boise State University in 2015, and the University of Utah in 2016. 
Finally, we thank the University of Utah for hosting a collaborative development visit in 2018, and the Institute of Mathematics and its Applications for its support for a Coding Sprint in 2019, where the current version of the package was finalized and this paper was completed.
